Modeling the Linux page cache for accurate simulation of data-intensive applications

### 2020-12-17 paper_io_sim.tex
Update nighres results

        The real application was a workflow of the Nighres
        toolbox~\cite{huntenburg2018nighres}, implementing cortical
        reconstruction from brain images in four steps: skull stripping,
        tissue classification, region extraction, and cortical
        reconstruction. Each step read
        files produced by the previous step, and wrote files that were or were not read by the subsequent step. 
        More information on this
        application is available in the Nighres documentation at
        \url{https://nighres.readthedocs.io/en/latest/auto_examples/example_02_cortical_depth_estimation.html}.
        The application is implemented as a Python script that calls Java
        image-processing routines. We used Python 3.6, Java 8, and Nighres
        1.3.0. We patched the application to remove lazy data loading,
        which made CPU time difficult to separate from I/O time, and to
        monitor task CPU times, to inject them in the simulators. The
        patched code is available at
        \url{https://github.com/dohoangdzung/nighres}.
        \begin{table}[t]
            \centering
            \begin{tabular}{lccc}
            \toprule
                \multicolumn{1}{c}{Workflow step}& Input size       & Output size      & CPU time\\
                                       & (MB)             & (MB)             & (s)\\
            \midrule
               Skull stripping         &  111             & 30               & 137 \\
               Tissue classification   &  22              & 175              & 624 \\
               Region extraction       &  175             & 121              & 81 \\
               Cortical reconstruction &  47              & 250              & 270\\
            \bottomrule
            \end{tabular} 
            \caption{Nighres application parameters}
            \label{table:nighres_stats}
            \end{table}
            \begin{table}[b]
                \centering
                \begin{tabularx}{\columnwidth}{ll
                >{\centering\arraybackslash}X
                >{\centering\arraybackslash}X
                >{\centering\arraybackslash}X}
                \toprule
                    \multicolumn{2}{c}{Bandwidths}  & Cluster (real) & Python prototype & \wrench simulator\\
                \midrule
                \multirow{2}{*}{Memory}      & read  & 6860 & 4812 & 4812\\
                                             & write & 2764 & 4812 & 4812\\
                \multirow{2}{*}{Local disk}  & read  & 510  & 465  & 465\\
                                             & write & 420  & 465  & 465\\
                \multirow{2}{*}{Remote disk} & read  & 515  & -    & 445\\
                                             & write & 375  & -    & 445\\
                \multicolumn{2}{l}{Network}  & 3000  & -    & 3000\\
                \bottomrule
                \end{tabularx}
                \caption{Bandwidth benchmarks (MBps) and simulator configurations.
                The bandwidths used in the simulations were the average of the measured read and write bandwidths.
                Network accesses were not simulated in the Python prototype.}
                \label{table:benchmark}
                \end{table}

@@

        \subsection{Real application (Exp 4)}
        As for the synthetic application, simulation errors were
        substantially reduced by the WRENCH-cache simulator compared to
        WRENCH (Figure~\ref{fig:nighres}). On average, errors were reduced
        from 212~\% in WRENCH to 68~\% in WRENCH-cache. Error
        reduction was mostly due to read times, since write
        times remained generally identical between both implementations, presumably due to 
        the dominance of file compression time in write time.
        Similar to
        the synthetic application, the first read happened entirely from disk and was therefore 
        very accurately simulated by both WRENCH and WRENCH-cache.

>>>>

        The real application was a workflow of the Nighres
        toolbox~\cite{huntenburg2018nighres}, implementing cortical
        reconstruction from brain images in four steps: skull stripping,
        tissue classification, region extraction, and cortical
        reconstruction. Each step read
        files produced by the previous step, and wrote files that were or were not read by the subsequent step. 
        More information on this
        application is available in the Nighres documentation at
        \url{https://nighres.readthedocs.io/en/latest/auto_examples/example_02_cortical_depth_estimation.html}.
        The application is implemented as a Python script that calls Java
        image-processing routines. We used Python 3.6, Java 8, and Nighres
        1.3.0. We patched the application to remove lazy data loading,
        which made CPU time difficult to separate from I/O time, and to
        monitor task CPU times, to inject them in the simulators. The
        patched code is available at
        \url{https://github.com/dohoangdzung/nighres}.
        \begin{table}[t]
            \centering
            \begin{tabular}{lccc}
            \toprule
                \multicolumn{1}{c}{Workflow step}& Input size       & Output size      & CPU time\\
                                       & (MB)             & (MB)             & (s)\\
            \midrule
               Skull stripping         &  295             & 393               & 137 \\
               Tissue classification   &  197              & 1376              & 614 \\
               Region extraction       &  1376             & 885              & 76 \\
               Cortical reconstruction &  393              & 786              & 272\\
            \bottomrule
            \end{tabular} 
            \caption{Nighres application parameters}
            \label{table:nighres_stats}
            \end{table}
            \begin{table}[b]
                \centering
                \begin{tabularx}{\columnwidth}{ll
                >{\centering\arraybackslash}X
                >{\centering\arraybackslash}X
                >{\centering\arraybackslash}X}
                \toprule
                    \multicolumn{2}{c}{Bandwidths}  & Cluster (real) & Python prototype & \wrench simulator\\
                \midrule
                \multirow{2}{*}{Memory}      & read  & 6860 & 4812 & 4812\\
                                             & write & 2764 & 4812 & 4812\\
                \multirow{2}{*}{Local disk}  & read  & 510  & 465  & 465\\
                                             & write & 420  & 465  & 465\\
                \multirow{2}{*}{Remote disk} & read  & 515  & -    & 445\\
                                             & write & 375  & -    & 445\\
                \multicolumn{2}{l}{Network}  & 3000  & -    & 3000\\
                \bottomrule
                \end{tabularx}
                \caption{Bandwidth benchmarks (MBps) and simulator configurations.
                The bandwidths used in the simulations were the average of the measured read and write bandwidths.
                Network accesses were not simulated in the Python prototype.}
                \label{table:benchmark}
                \end{table}

@@

        \subsection{Real application (Exp 4)}
        As for the synthetic application, simulation errors were
        substantially reduced by the WRENCH-cache simulator compared to
        WRENCH (Figure~\ref{fig:nighres}). On average, errors were reduced
        from 337~\% in WRENCH to 47~\% in WRENCH-cache. 
%        Error reduction was mostly due to read times, since write
%        times remained generally identical between both implementations, presumably due to 
%        the dominance of file compression time in write time.
        Similar to
        the synthetic application, the first read happened entirely from disk and was therefore 
        very accurately simulated by both WRENCH and WRENCH-cache.
